# Characteristics of Fixed Effects Variables for Mixed Models

```{r}
#| label: setup
#| include: false

source("R/setup-script.R")
```

The following code reproduces the factor coding and descriptive statistics reported in Table 3 of the main text.

## Dependent Variables

```{r}
#| label: dep-var
#| output: asis

for (p in str_perception_levels) {
  cat(paste0("#### ", p, "\n\n"))

  df <- data_rq1 %>%
    filter(perception == p) %>%
    group_by(Timepoint) %>%
    get_summary_stats(rating, type = "common") %>%
    mutate(across(c(mean, sd), ~ scales::number(.x, accuracy = .01)))

  print(kable(df))

  cat("\n")

  rm(p, df)
}
```

## Covariates

### Cohort

```{r}
#| label: covariates
data_rq1$Cohort %>%
  contrasts() %>%
  as_tibble(rownames = "Factor Levels") %>%
  round_all_doubles()
```

### Semester Week

```{r}
#| label: semester-week
data_rq1 %>%
  select(Participant, Semester_Week) %>%
  unique() %>%
  get_summary_stats(Semester_Week, type = "common")
```

### Test Version

```{r}
#| label: test-version
data_rq1$Test_Version %>%
  contrasts() %>%
  as_tibble(rownames = "Factor Levels") %>%
  round_all_doubles()
```

### Item-Level Accuracy

Factor Coding:

```{r}
#| label: accuracy-factor
data_rq1$`Item-Level Accuracy` %>%
  contrasts() %>%
  as_tibble(rownames = "Factor Levels") %>%
  round_all_doubles()
```

Baseline and Posttest Means and Standard Deviations:

```{r}
#| label: accuracy-num
data_rq1 %>%
  select(Participant, Timepoint, Item, Accuracy_Raw) %>%
  unique() %>%
  group_by(Timepoint) %>%
  get_summary_stats(type = "common") %>%
  mutate(across(c(mean, sd), ~ scales::number(.x, accuracy = .01)))
```

### Baseline Threat

```{r}
#| label: baseline-threat
data_rq1 %>%
  select(Participant, Baseline_Threat) %>%
  unique() %>%
  get_summary_stats(Baseline_Threat, type = "common")
```

## Main Independent Variables of Interest

### Timepoint

```{r}
#| label: timepoint
data_rq1$Timepoint %>%
  contrasts() %>%
  as_tibble(rownames = "Factor Levels")
```

### Condition

```{r}
#| label: condition
data_rq1$Condition %>%
  contrasts() %>%
  as_tibble(rownames = "Factor Levels")
```

### Gender

```{r}
#| label: gender
data_rq1$Gender %>%
  contrasts() %>%
  as_tibble(rownames = "Factor Levels") %>%
  round_all_doubles()
```


